Pillar 2 - Topic Modeling

### 2019-03-01 Pillar_2_-_Topic_Modeling.Rmd
comment for jerry

@@

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data}
load("output/data_pillar_2.RDATA")

@@

# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data){

>>>>

COMMENTS: 
Q. Jerry -> For preprocessing (selecting vocabulary), how do we assign words that appear in only one document to a topic? Does it make sense to remove them?

@@

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the list `d_text`, and the datasets `d_course` and `d_transcript`.
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data}
load("output/data_pillar_2.RDATA")

@@

To prepare the output of pillar two, we will need d_course. Thus we load the environment `output/data_pillar_1.RDATA`. It contains the datasets d_course and d_transcript.
```{r}
#
##Import d_course and d_transcript
load("Output/data_pillar_1.RDATA")
```
# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data){
